sdmTMB: an R package for fast, flexible, and accessible generalized linear mixed effects models with spatial and spatiotemporal random fields

### 2022-07-21 doc/paper.Rmd
Edit?

    | 2. Here, we introduce the R package sdmTMB, which extends the flexible interface familiar to users of glm(), lme4, glmmTMB, or mgcv to include spatial and spatiotemporal latent fields using a predictive-process SPDE- (stochastic partial differential equation) approach. Estimation is conducted via maximum marginal likelihood with Template Model Builder (TMB), although penalised likelihood and Bayesian inference (via tmbstan/Stan) are also possible. We describe the statistical model, illustrate the package's use to advance research and monitoring through two case studies, and compare the functionality, speed, and interface to related software.

>>>>

    | 2. Here, we introduce the R package sdmTMB, which extends the flexible interface familiar to users of glm(), lme4, glmmTMB, or mgcv to include spatial and spatiotemporal latent fields using a predictive-process SPDE-(stochastic partial differential equation) based approach. Estimation is conducted via maximum marginal likelihood with Template Model Builder (TMB), although penalised likelihood and Bayesian inference (via tmbstan/Stan) are also possible. We describe the statistical model, illustrate the package's use to advance research and monitoring through two case studies, and compare the functionality, speed, and interface to related software.
